VM-Centric Snapshot Deduplication with Fault Isolation for Converged Cloud Architectures

### 2014-07-17 snapshot_system/paper_dedup.tex
r

Compared to ~\cite{bottleneck08}, the fingerprint index  size is reduced by $1-\sigma$
and the searchable fingerprint space  becomes very small under the popularity constraint.  
The fingerprint-guided distributed mapping in ~\cite{extreme_binning09,Dong2011} narrows
the search scope of each data chunk, but it does not reduce th total amount of searchable fingerprints
used for the entire deduplication. 
%In comparison we only focus on top popular chunks among VMs and this
%significantly reduces the total amount of  searchable fingerprints.

>>>>

Compared to ~\cite{bottleneck08}, the fingerprint index  size is reduced by $1-\sigma$
and the searchable fingerprint space  becomes very small under the popularity constraint.  
The fingerprint-guided distributed mapping in ~\cite{extreme_binning09,Dong2011} narrows
the search scope of each data chunk, but it does not reduce th total amount of searchable fingerprints
used for the entire deduplication. 
%In comparison we only focus on top popular chunks among VMs and this
%significantly reduces the total amount of  searchable fingerprints. 
We have not adopted the index sampling in \cite{Guo2011} because its extension for
for a distributed architecture is difficult.  To use a distributed memory version of the sampled index, every deduplication 
request may access a remote machine for index lookup and the overall overhead of access latency for all requests
can be significant.
